\emph{MixFishSim}: highly resolved spatiotemporal simulations for exploring mixed fishery dynamics

### 2019-01-24 write_up/mixfishsim_ecolmod.tex
Bug fix in the real_pop closures on a monthly timescale - wasn't filtering, is now!

\usepackage{lineno,hyperref}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{amsfonts}
\usepackage{mathtools}
\usepackage{tikz}
\usetikzlibrary{shapes,arrows,chains,calc}
\usepackage{hhline}
\usepackage{booktabs}
\usepackage[textsize=scriptsize]{todonotes}
%\usepackage[textsize=scriptsize, disable]{todonotes}  %% to turn off notes
\usepackage{eurosym}

% For track-changes
\usepackage[draft]{changes}
%\usepackage[final]{changes} %% to turn off changes
\definechangesauthor[color = red]{JM}
\definechangesauthor[color = blue]{PD}
\definechangesauthor[color = green!40!black]{JJ}
\definechangesauthor[color = purple]{CM}

@@

\replaced[id = PD]{If fisheries are to avoid unwanted catch}{To implement
	effective spatial measures to reduce discards} a good understanding of
spatiotemporal fishery dynamics is required. However, traditional scientific
advice is limited by a lack of highly resolved knowledge of population
distributions, movement and how fishers interact with different fish
populations. This reflects the fact that data on fish location at high temporal
and spatial resolutions is expensive and difficult to collect. Proxies inferred
from either scientific surveys or commercial catch data are often used to model
distributions, often with sparse data at limited spatial and temporal
resolution. \\

@@

We simulate 50 years of fishing and use the results from the fisheries catch to
draw inference on the underlying population structures. We compare this
inference to i) a simulated fixed-site sampling design commonly used for
fisheries monitoring purposes, and ii) the true underlying population
structures input to the simulation, to establish the potential and limitations
of fishery-dependent data - an inherently biased sampling method due to
fisher's targeting- to provide a robust picture of spatiotemporal
distributions. Finally, we simulate an area closure based on areas defined from
the known ("real-population") distribution, commercial catch data and survey
data at different temporal and spatial resolutions and assess their
effectiveness on reducing catches of a fish population. \\

@@

\begin{table}[!ht]
\caption{Population dynamics and movement parameter setting}
	\begin{tabular}{ p{4cm } p{2cm} p{2cm} p{2cm} p{2cm}}
	Parameter & Pop 1 & Pop 2 & Pop 3 & Pop 4 \\
	\hline
	Habitat quality & & & \\
	\hline
	Matérn $\nu$ & 1/0.15 & 1/0.05 & 1/0.55 & 1/0.05  \\
	Matérn $\kappa$ & 1 & 2 & 1 & 1  \\
	Anisotropy & 1.5,3,-3,4 & 1,2,-1,2 & 2.5,1,-1,2 & 0.1,2,-1,0.2 \\
	Spawning areas (bound box) & 40,50,40,50; 80,90,60,70 &
	50,60,30,40; 80,90,90,90 & 30,34,10,20; 60,70,20,30 & 50,55,80,85; 30,40,30,40 \\
	Spawning multiplier & 10 & 10 & 10 & 10 \\
	Movement $\lambda$ & 0.3 & 0.3 & 0.3 & 0.3 \\
	\hline
	Population dynamics & & & & \\
	\hline
	Starting Biomass & 1e5 & 2e5 & 1e5 & 1e4 \\
	Beverton-Holt Recruit 'a' & 60 & 100 & 80 & 2 \\
	Beverton-Holt Recruit 'b' & 250 & 250 & 200 & 50 \\
	Beverton-Holt Recruit $\sigma^2$ & 0.4 & 0.3 & 0.4 & 0.3 \\
	Recruit week & 13-16 & 12-16 & 14-16 & 16-20 \\
	Spawn week & 16-18 & 16-19 & 16-18 & 18-20 \\
	$K$ & 0.3 & 0.3 & 0.3 & 0.3 \\
	$wt$ & 1 & 1 & 1 & 1 \\
	$wt_{d-1}$ & 0.1 & 0.1 & 0.1 & 0.1 \\
	M (annual) & 0.2 & 0.2 & 0.2 & 0.1 \\
	\hline
\end{tabular}
\label{tab:1}
\end{table}

\begin{table}[!ht]
\caption{Fleet dynamics parameter setting}
\begin{tabular}{ p{4cm } p{1cm} p{1cm} p{1cm} p{1cm} p{1cm}}
	\hline
	Parameter & Fleet 1 & Fleet 2 & Fleet 3 & Fleet 4 & Fleet 5 \\
	\hline
	Targeting preferences &&&& \\
	\hline
	Price Pop1 & 100 & 100 & 100 & 100 & 100 \\
	Price Pop2 & 200 & 200 & 200 & 200 & 200 \\
	Price Pop3 & 600 & 600 & 600 & 600 & 600 \\
	Price Pop4 & 1600 & 1600 & 1600 & 1600 & 1600 \\
	$Q$ Pop1 & 0.01 & 0.02 & 0.02 & 0.01 & 0.01 \\
	$Q$ Pop2 & 0.02 & 0.01 & 0.02 & 0.01 & 0.03\\
	$Q$ Pop3 & 0.01 & 0.02 & 0.02 & 0.01 & 0.02 \\
	$Q$ Pop4 & 0.02 & 0.01 & 0.02 & 0.05 & 0.01 \\
	\hline
	Exploitation dynamics &&&& \\
	\hline
	step function $\beta_1$ & 1 & 2 & 1 & 2 & 3 \\
	step function $\beta_2$ & 10 & 10 & 8 & 12 & 7 \\
	step function $\beta_3$ & Q90 & Q90 & Q85 & Q90 & Q80 \\
	step function $rate$ & 10 & 20 & 15 & 25 & 10 \\
	Past Knowledge & T & T & T & T & T \\
	Past Year \& Month & T & T & T & T & T \\
	Past Trip & T & T & T & T & T \\
	Threshold & 0.75 & 0.75 & 0.75 & 0.75 & 0.75 \\
	\hline
\end{tabular}
\label{tab:2}
\end{table}

>>>>

\usepackage{lineno,hyperref}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{amsfonts}
\usepackage{mathtools}
\usepackage{tikz}
\usetikzlibrary{shapes,arrows,chains,calc}
\usepackage{hhline}
\usepackage{booktabs}
%\usepackage[textsize=scriptsize]{todonotes}
\usepackage[textsize=scriptsize, disable]{todonotes}  %% to turn off notes
\usepackage{eurosym}

% For track-changes
%\usepackage[draft]{changes}
\usepackage[final]{changes} %% to turn off changes
\definechangesauthor[color = red]{JM}
\definechangesauthor[color = blue]{PD}
\definechangesauthor[color = green!40!black]{JJ}
\definechangesauthor[color = purple]{CM}

@@

\replaced[id = PD]{If fisheries are to avoid unwanted catch}{To implement
	effective spatial measures to reduce discards} a good understanding of
spatiotemporal fishery dynamics is required. However, traditional scientific
advice is limited by a lack of highly resolved knowledge of population
distributions, population movement and how fishers interact with different fish
populations. This reflects the fact that data on fish location at high temporal
and spatial resolutions is expensive and difficult to collect. Proxies inferred
from either scientific surveys or commercial catch data are often used to model
distributions, often with sparse data at limited spatial and temporal
resolution. \\

@@

We simulate 50 years of fishing and use the results from the fisheries catch to
draw inference on the underlying population structures. We compare this
inference to i) a simulated fixed-site sampling design commonly used for
fisheries monitoring purposes, and ii) the true underlying population
structures input to the simulation. We use the results to establish the
potential and limitations of fishery-dependent data - an inherently biased
sampling method due to fisher's targeting- to provide a robust picture of
spatiotemporal distributions. Finally, we simulate an area closure based on
areas defined from the known ("real-population") distribution, commercial catch
data and survey data at different temporal and spatial resolutions and assess
their effectiveness on reducing catches of a fish population. \\

@@

\begin{table}[!ht]
\caption{Population dynamics and movement parameter setting}
	\begin{tabular}{ p{4cm } p{2cm} p{2cm} p{2cm} p{2cm}}
	Parameter & Pop 1 & Pop 2 & Pop 3 & Pop 4 \\
	\hline
	Habitat quality & & & \\
	\hline
	Matérn $\nu$ & 1/0.015 & 1/0.05 & 1/0.01 & 1/0.005  \\
	Matérn $\kappa$ & 1 & 2 & 1 & 1  \\
	Anisotropy & 1.5,3,-3,4 & 1,2,-1,2 & 2.5,1,-1,2 & 0.1,2,-1,0.2 \\
	Spawning areas (bound box) & 40,50,40,50; 80,90,60,70 &
	50,60,30,40; 80,90,90,90 & 30,34,10,20; 60,70,20,30 & 50,55,80,85; 30,40,30,40 \\
	Spawning multiplier & 10 & 10 & 10 & 10 \\
	Movement $\lambda$ & 0.1 & 0.1 & 0.1 & 0.1 \\
	\hline
	Population dynamics & & & & \\
	\hline
	Starting Biomass & 1e5 & 2e5 & 1e5 & 1e4 \\
	Beverton-Holt Recruit 'a' & 6 & 27 & 18 & 0.3  \\
	Beverton-Holt Recruit 'b' & 4 & 4 & 11 & 0.5 \\
	Beverton-Holt Recruit $\sigma^2$ & 0.7 & 0.6 & 0.7 & 0.6 \\
	Recruit week & 13-16 & 12-16 & 14-16 & 16-20 \\
	Spawn week & 16-18 & 16-19 & 16-18 & 18-20 \\
	$K$ & 0.3 & 0.3 & 0.3 & 0.3 \\
	$wt$ & 1 & 1 & 1 & 1 \\
	$wt_{d-1}$ & 0.1 & 0.1 & 0.1 & 0.1 \\
	M (annual) & 0.2 & 0.1 & 0.2 & 0.1 \\
	\hline
	Movement dynamics & & & & \\
	\hline
	$\mu$ & 12 & 15 & 17 & 14 \\
	$\sigma^2$ & 8 & 9 & 7 & 10 \\
	\hline
\end{tabular}
\label{tab:1}
\end{table}

\begin{table}[!ht]
\caption{Fleet dynamics parameter setting}
\begin{tabular}{ p{4cm } p{1cm} p{1cm} p{1cm} p{1cm} p{1cm}}
	\hline
	Parameter & Fleet 1 & Fleet 2 & Fleet 3 & Fleet 4 & Fleet 5 \\
	\hline
	Targeting preferences &&&& \\
	\hline
	Price Pop1 & 100 & 100 & 100 & 100 & 100 \\
	Price Pop2 & 200 & 200 & 200 & 200 & 200 \\
	Price Pop3 & 350 & 350 & 350 & 350 & 350 \\
	Price Pop4 & 600 & 600 & 600 & 600 & 600 \\
	$Q$ Pop1 & 0.01 & 0.02 & 0.02 & 0.01 & 0.01 \\
	$Q$ Pop2 & 0.02 & 0.01 & 0.02 & 0.01 & 0.03\\
	$Q$ Pop3 & 0.01 & 0.02 & 0.02 & 0.01 & 0.02 \\
	$Q$ Pop4 & 0.02 & 0.01 & 0.02 & 0.05 & 0.01 \\
	\hline
	Exploitation dynamics &&&& \\
	\hline
	step function $\beta_1$ & 1 & 2 & 1 & 2 & 3 \\
	step function $\beta_2$ & 10 & 15 & 8 & 12 & 7 \\
	step function $\beta_3$ & Q90 & Q90 & Q85 & Q90 & Q80 \\
	step function $rate$ & 20 & 30 & 25 & 35 & 20 \\
	Past Knowledge & T & T & T & T & T \\
	Past Year \& Month & T & T & T & T & T \\
	Past Trip & T & T & T & T & T \\
	Threshold & 0.7 & 0.7 & 0.7 & 0.7 & 0.7 \\
	Fuel Cost & 3 & 2 & 5 & 2 & 1 \\
	\hline
\end{tabular}
\label{tab:2}
\end{table}
